Project-plan

### 2025-10-10 project-plan.qmd
Changing definition of GCS

---
title: "project-plan"
date: today 
bibliography: bibliography.bib
csl: vancouver.csl
format: html
---
<!-- CP: The report is interesting, very promising and also well written. 
Effort is needed to further improve the report by structuring it in relation to the aims. Aims also to be improved according to the course i.e. challenging a scientific question (possibly having a hypothesis) in a yes/no manner: see comments
I might have missed some points in the report not being a clinician working on this matter but I think that you can improve the structure of the Aims and M&M a bit more. -->

@@

Pathophysiology 
------------

Among trauma-related conditions, traumatic brain injury (TBI) is a major cause of death and disability worldwide and
constitutes a significant public health burden [@Guan2023]. TBI is the result of an external force causing
neurological impairments that may be either transient or permanent [@Capizzi2020]. Furthermore, TBI should not be
regarded as a single event but rather as a dynamic process. The initial trauma often triggers a secondary
pathophysiological cascade, including ischemia, oedema, and metabolic disturbances, that develop over time and
critically influence long-term outcomes [@Robba2025]. As such, patients with TBI often require admission to the
intensive care unit (ICU).

Management of TBI 
------------

<!-- MGW: Consider discussing the management of trauma first and then the management of TBI, as many of the things you write below also apply to non-TBI trauma patients -->

@@

Statistical methods. <!-- CP: Pls recall aim 1 and aim 2 and develop the below text in relation to these 2 aims: see criteria-->
----------------

>>>>

---
title: "Project-plan"
date: today 
bibliography: bibliography.bib
csl: vancouver.csl
format: html
---
<!-- CP: The report is interesting, very promising and also well written. 
Effort is needed to further improve the report by structuring it in relation to the aims. Aims also to be improved according to the course i.e. challenging a scientific question (possibly having a hypothesis) in a yes/no manner: see comments
I might have missed some points in the report not being a clinician working on this matter but I think that you can improve the structure of the Aims and M&M a bit more. -->

@@

Pathophysiology 
------------
Among trauma-related conditions, traumatic brain injury (TBI) is a major cause of death and disability worldwide and
constitutes a significant public health burden [@Guan2023]. TBI is the result of an external force causing
neurological impairments that may be either transient or permanent [@Capizzi2020]. Furthermore, TBI should not be
regarded as a single event but rather as a dynamic process. The initial trauma often triggers a secondary
pathophysiological cascade, including ischemia, oedema, and metabolic disturbances, that develop over time and
critically influence long-term outcomes [@Robba2025]. As such, patients with TBI often require admission to the
intensive care unit (ICU).

Management of TBI 
------------
<!-- MGW: Consider discussing the management of trauma first and then the management of TBI, as many of the things you
write below also apply to non-TBI trauma patients -->

@@

Statistical methods. <!-- CP: Pls recall aim 1 and aim 2 and develop the below text in relation to these 2 aims: see criteria-->
----------------
<!-- Write that there will be descripitve analysis for OFI prevelance...-->
